---
title: "Reallocations of Sleep, Physical activity, Sedentary behaviour are Associated with Mental Health Differently by Insomnia: A UK Biobank Cohort Study"
author: Flora Le (flora.le@monash.edu, floralebui@gmail.com)
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: yes
    toc_float: yes
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 8
    fig_height: 5
    fig_caption: yes
    number_sections: true
---

This file presents the supplementary
materials of the manuscript:
**Reallocations of Sleep, Physical activity, Sedentary behaviour are Associated with Mental Health Differently by Insomnia: A UK Biobank Cohort Study**.

```{r, echo=FALSE, message=FALSE}
source("ukb-24h-mh-supp.R")
```

# Outcome Distributions
* Depressive symptoms

```{r, warning=FALSE, echo=FALSE}
phq_2023_hist
```

* Anxiety symptoms

```{r, warning=FALSE, echo=FALSE}
gad_2023_hist
```

# Sensitivity analyses
*Notes*. All estimates are relative to the mean behaviour composition. 
MVPA = moderate-to-vigorous physical activity, LPA = light physical activity, SB = sedentary behaviour. 
Models adjusted for age, sex, ethnicity, education attainment, working status, smoking status, drinking status, deprivation. 
Values are posterior means and 95% credible intervals.

## Depressive symptoms
### Associations in individuals with prior incident depression and anxiety
#### Main sample

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_dep_anx[[1]])
```

#### By insomnia symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_dep_anx_insomnia[[1]])
```

<!-- ### Associations by BMI -->
<!-- #### Main sample -->
<!-- ##### Under to Normal weight (< 25 kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_healthy[[1]]) -->
<!-- ``` -->

<!-- ##### Overweight (25.0–29.9 kg/ m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_overweight[[1]]) -->
<!-- ``` -->

<!-- ##### Obese (30+ kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_obese[[1]]) -->
<!-- ``` -->

<!-- ### Associations by insomnia -->
<!-- #### Under to Normal weight (< 25 kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_healthy_insomnia[[1]]) -->
<!-- ``` -->

<!-- #### Overweight (25.0–29.9 kg/ m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_overweight_insomnia[[1]]) -->
<!-- ``` -->

<!-- #### Obese (30+ kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_obese_insomnia[[1]]) -->
<!-- ``` -->

## Anxiety symptoms
### Associations in individuals with prior incident depression and anxiety
#### Main sample

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_dep_anx[[2]])
```

#### By insomnia symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_dep_anx_insomnia[[2]])
```

<!-- ### Associations by BMI -->
<!-- #### Main sample -->
<!-- ##### Under to Normal weight (< 25 kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_healthy[[2]]) -->
<!-- ``` -->

<!-- ##### Overweight (25.0–29.9 kg/ m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_overweight[[2]]) -->
<!-- ``` -->

<!-- ##### Obese (30+ kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_obese[[2]]) -->
<!-- ``` -->

<!-- #### By insomnia symptoms -->
<!-- ##### Under to Normal weight (< 25 kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_healthy_insomnia[[2]]) -->
<!-- ``` -->

<!-- ##### Overweight (25.0–29.9 kg/ m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_overweight_insomnia[[2]]) -->
<!-- ``` -->

<!-- ##### Obese (30+ kg/m2) -->

<!-- ```{r, warning=FALSE, echo=FALSE, fig.width=9} -->
<!-- knitr::kable(sub_models_obese_insomnia[[2]]) -->
<!-- ``` -->
