---
title: "Reallocations of Sleep, Physical activity, Sedentary behaviour are Associated with Mental Health Differently by Insomnia: A UK Biobank Cohort Study"
author: Flora Le (flora.le@monash.edu or floralebui@gmail.com)
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: yes
    toc_float: yes
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 8
    fig_height: 7
    fig_caption: yes
    number_sections: true
---

This file presents the supplementary
materials of the manuscript
**Reallocations of Sleep, Physical activity, Sedentary behaviour are Associated with Mental Health Differently by Insomnia: A UK Biobank Cohort Study** by *Flora Le, Dorothea Dumuid, Josh Leota, Anya Topiwala, Daniel J. Smith, Tyman E. Stanford, Aiden Doherty, and Joshua F. Wiley*.

```{r, echo=FALSE, message=FALSE}
source("ukb-24h-mh-supp.R")
```

# Outcome Distributions
*Notes*. Top panels show full sample, bottom panels show sub sample of individuals with scores > 10 
(cut-off for possible clinical diagnoses).
Vertical dashed lines show the sample average.

## Depressive symptoms

```{r, warning=FALSE, echo=FALSE}
phq_2023_hist
```

## Anxiety symptoms

```{r, warning=FALSE, echo=FALSE}
gad_2023_hist
```

# Sensitivity analyses
*Notes*. All estimates are relative to the mean behaviour composition. 
MVPA = moderate-to-vigorous physical activity, LPA = light physical activity, SB = sedentary behaviour. 
Models adjusted for age, sex, ethnicity, education attainment, working status, smoking status, drinking status, deprivation. 
Values are posterior means and 95% credible intervals.

## Repeated analyses in individuals with prior incident depression and anxiety
### Main sample
#### Depressive symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_dep_anx[[1]])
```

#### Anxiety symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_2016[[2]])
```

### By insomnia symptoms
#### Depressive symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_dep_anx_insomnia[[1]])
```

#### Anxiety symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_dep_anx_insomnia[[2]])
```

## Repeated analyses using Mental Health Questionnaire (2016-2017)
### Main sample
#### Depressive symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_2016[[1]])
```

#### Anxiety symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_2016[[2]])
```

### By insomnia symptoms
#### Depressive symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_2016_insomnia[[1]])
```

#### Anxiety symptoms

```{r, warning=FALSE, echo=FALSE, fig.width=9}
knitr::kable(sub_models_2016_insomnia[[2]])
```
