---
title: "UK Biobank Movement Behaviours and Mental Health"
author: "Flora Le (flora.le@monash.edu)"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: spacelab
    highlight: zenburn
    toc: no
    toc_float: no
    collapsed: no
    smooth_scroll: no
    toc_depth: 4
    fig_width: 9
    fig_height: 12
    fig_caption: yes
    number_sections: true
---

This file presents the supplementary materials for the manuscript:

**Reallocation of Time Between Sleep, Physical Activity, and Sedentary Behaviour and Mental Health in > 90,000 Individuals**.

```{r, echo=FALSE, message=FALSE}
source("ukb-24h-mh-supp.R")
```

# Statistics for 20-minute Reallocations

### Under to normal weight (BMI < 25)

```{r, warning=FALSE, messages = FALSE, echo = FALSE, results='asis', fig.align='center'}

```

### Overweight (25 < BMI < 30)

```{r, warning=FALSE, messages = FALSE, echo = FALSE, results='asis', fig.align='center'}

```

### Obese (BMI > 30)

```{r, warning=FALSE, messages = FALSE, echo = FALSE, results='asis', fig.align='center'}

```
# Visualisation of Reallocation from 1 to 20 minutes of Movement Behaviours, stratified by BMI
## Depressive Symptoms
### Under to normal weight (BMI < 25)

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
figure <- ggarrange(phq_24h_healthy[[1]], phq_24h_healthy[[2]], 
                    phq_24h_healthy[[3]], phq_24h_healthy[[4]], 
                    nrow = 4,
                    common.legend = TRUE,
                    legend   = "bottom"
)
annotate_figure(figure, 
                left = text_grob("Estimated Difference in Depressive Symptoms", size = 14, rot = 90, family = "Arial Narrow", face = "bold"))
```

### Overweight (25 < BMI < 30)

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
figure <- ggarrange(phq_24h_overweight[[1]], phq_24h_overweight[[2]], 
                    phq_24h_overweight[[3]], phq_24h_overweight[[4]], 
                    nrow = 4,
                    common.legend = TRUE,
                    legend   = "bottom"
)
annotate_figure(figure,
                left = text_grob("Estimated Difference in Depressive Symptoms", size = 14, rot = 90, family = "Arial Narrow", face = "bold"))
```

### Obese (BMI > 30)

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
figure <- ggarrange(phq_24h_obese[[1]], phq_24h_obese[[2]], 
                    phq_24h_obese[[3]], phq_24h_obese[[4]], 
                    nrow = 4,
                    common.legend = TRUE,
                    legend   = "bottom"
)
annotate_figure(figure, 
                left = text_grob("Estimated Difference in Depressive Symptoms", size = 14, rot = 90, family = "Arial Narrow", face = "bold"))
```

## Anxiety Symptoms
### Under to normal weight (BMI < 25)

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
figure <- ggarrange(gad_24h_healthy[[1]], gad_24h_healthy[[2]], 
                    gad_24h_healthy[[3]], gad_24h_healthy[[4]], 
                    nrow = 4,
                    common.legend = TRUE,
                    legend   = "bottom"
)
annotate_figure(figure,
                left = text_grob("Estimated Difference in Anxiety Symptoms", size = 14, rot = 90, family = "Arial Narrow", face = "bold"))
```

### Overweight (25 < BMI < 30)

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
figure <- ggarrange(gad_24h_overweight[[1]], gad_24h_overweight[[2]], 
                    gad_24h_overweight[[3]], gad_24h_overweight[[4]], 
                    nrow = 4,
                    common.legend = TRUE,
                    legend   = "bottom"
)
annotate_figure(figure,
                left = text_grob("Estimated Difference in Anxiety Symptoms", size = 14, rot = 90, family = "Arial Narrow", face = "bold"))
```

### Obese (BMI > 30)

```{r, warning=FALSE, echo = FALSE, results='asis', fig.align='center'}
figure <- ggarrange(gad_24h_obese[[1]], gad_24h_obese[[2]], 
                    gad_24h_obese[[3]], gad_24h_obese[[4]], 
                    nrow = 4,
                    common.legend = TRUE,
                    legend   = "bottom"
)
annotate_figure(figure,
                left = text_grob("Estimated Difference in Anxiety Symptoms", size = 14, rot = 90, family = "Arial Narrow", face = "bold"))
```